Variational Inference for Inverse Reinforcement Learning with Gaussian Processes

### 2019-03-16 mpaper/paper.tex
All the important information should be there, but in a very messy form

\newcommand{\Kuu}{\mathbf{K}_{\mathbf{u},\mathbf{u}}}
\newcommand{\Krr}{\mathbf{K}_{\mathbf{r},\mathbf{r}}}
\newcommand{\Kru}{\mathbf{K}_{\mathbf{r},\mathbf{u}}}
\newcommand{\Luu}{\mathbf{L}_{\mathbf{u},\mathbf{u}}}

@@

\subsection{Theoretical Justification}

@@

  TODO: Show that $\bm\Gamma^{-1}|_{\lambda_i = c(\mathbf{r}, \mathbf{u})}$ is
  bounded. Might need something similar to the matrix bound lemma, since the
  definition of $\bm\Gamma$ involves addition.

  Since we already know that $\bm\Gamma^{-1}|_{\lambda_i = c(\mathbf{r},
    \mathbf{u})}$ and $\det(\bm\Gamma)|_{\lambda_i = c(\mathbf{r}, \mathbf{u})}$
  are bounded, so is $\adj(\bm\Gamma) =
  \det(\bm\Gamma)\bm\Gamma^{-1}|_{\lambda_i = c(\mathbf{r}, \mathbf{u})}$. Thus,
  we have constant bounds on
  $|\bm\Gamma|^{-1}\tr(\mathbf{R}\adj(\bm\Gamma))|_{\lambda_i = c(\mathbf{r},
    \mathbf{u})}$, which means that
  \[
    \left. \frac{\partial q(\mathbf{r} \mid \mathbf{u})}{\partial \lambda_i}
    \right|_{\lambda_i = c(\mathbf{r}, \mathbf{u})}
  \]
  has the required bounds.
\end{proof}

>>>>

\newcommand{\Kuu}{\mathbf{K}_{\mathbf{u},\mathbf{u}}}
\newcommand{\Krr}{\mathbf{K}_{\mathbf{r},\mathbf{r}}}
\newcommand{\Kru}{\mathbf{K}_{\mathbf{r},\mathbf{u}}}
\newcommand{\Luu}{\mathbf{L}_{\mathbf{u},\mathbf{u}}}
\newcommand{\Euu}{\mathbf{E}_{\mathbf{u},\mathbf{u}}}
\newcommand{\Err}{\mathbf{E}_{\mathbf{r},\mathbf{r}}}
\newcommand{\Eru}{\mathbf{E}_{\mathbf{r},\mathbf{u}}}

@@

\subsection{Theoretical Justification}
% TODO: in this section, 'constant' means 'constant w.r.t. u and r'

@@

  % TODO: actually demonstrate this for the inverse
  Recall that
  \[
    \bm\Gamma = \Krr - \mathbf{S}\Kru = \Krr - \Kru^\intercal\Kuu^{-1}\Kru.
  \]
  We have already demonstrated that for $\mathbf{K} \in \{ \Krr, \Kru, \Kuu^{-1}
  \}$, $\lim_{\epsilon \to 0}\mathbf{K}|_{\lambda_i = c(\mathbf{r}, \mathbf{u})}
  = \mathbf{K}$. We can use a general fact that if $\lim_{x \to 0} f(x) = f$,
  then $f(x) = f + g(x)$ for some function $g$ such that $\lim_{x \to 0} g(x) =
  0$ to define matrices $\Err$, $\Eru$, and $\Euu$ such that
  \begin{alignat*}{3}
    \Krr|_{\lambda_i = c(\mathbf{r}, \mathbf{u})} &= \Krr + \Err, &&\Err \to
    \mathbf{O}_{|\mathcal{S}|}, \\
    \Kru|_{\lambda_i = c(\mathbf{r}, \mathbf{u})} &= \Kru + \Eru, \quad
    \text{and} \quad &&\Eru \to \mathbf{O}_{|\mathcal{S}|, m}, \\
    \Kuu^{-1}|_{\lambda_i = c(\mathbf{r}, \mathbf{u})} &= \Kuu^{-1} + \Euu,
    &&\Euu \to \mathbf{O}_{m}.
  \end{alignat*}
  as $\epsilon \to 0$. Then, $\bm\Gamma|_{\lambda_i = c(\mathbf{r}, \mathbf{u})}
  = \bm\Gamma + \mathbf{E}$, where
  \begin{align*}
    \mathbf{E} &= \Err - \Kru^\intercal\Kuu^{-1}\Eru - \Kru^\intercal\Euu(\Kru + \Eru) \\
               &- \Eru^\intercal(\Kuu^{-1} + \Euu)(\Kru + \Eru) \\
               &\to \mathbf{O}_{|\mathcal{S}|}
  \end{align*}
  as $\epsilon \to 0$. Thus, Lemma \ref{lemma:perturbation} shows that
  $\bm\Gamma^{-1}|_{\lambda_i = c(\mathbf{r}, \mathbf{u})}$ exists and provides
  constant bounds on its elements.

  Since we already know that $\bm\Gamma^{-1}|_{\lambda_i = c(\mathbf{r},
    \mathbf{u})}$ and $\det(\bm\Gamma)|_{\lambda_i = c(\mathbf{r}, \mathbf{u})}$
  are bounded, so is $\adj(\bm\Gamma) =
  \det(\bm\Gamma)\bm\Gamma^{-1}|_{\lambda_i = c(\mathbf{r}, \mathbf{u})}$. Thus,
  we have constant bounds on
  $|\bm\Gamma|^{-1}\tr(\mathbf{R}\adj(\bm\Gamma))|_{\lambda_i = c(\mathbf{r},
    \mathbf{u})}$, which means that
  \[
    \left. \frac{\partial q(\mathbf{r} \mid \mathbf{u})}{\partial \lambda_i}
    \right|_{\lambda_i = c(\mathbf{r}, \mathbf{u})}
  \]
  has the required bounds.
\end{proof}
% TOOD: epsilon should not be treated as a constant. Revise the whole theory
% section.
